\huge Open, privacy-preserving protocols for lawful surveillance

### 2016-02-29 paper/conc.tex
Added future work idea

For contact chaining, it may be possible to speed up our protocols by using
elliptic-curve cryptography instead of RSA.  It may also be interesting to 
generalize the differential-privacy approach of Kearns {\it et 
al.}~\cite{krwy-pnas16} so that it applies to indirect contacts as well as
direct contacts.

>>>>

For contact chaining, it may be possible to speed up our protocols by using
elliptic-curve cryptography instead of RSA. Additionally, our assumption that
all parties behave in an honest-but-curious manner might be weakened. By using
standard zero-knowledge proof techniques, it might be possible to create a version
of the protocols in Section~\ref{sec-chaining} which are resistant even to, for
example, a rogue agent maliciously modifying telecom-supplied data to falsely
incriminate a victim. It may also be interesting to 
generalize the differential-privacy approach of Kearns {\it et 
al.}~\cite{krwy-pnas16} so that it applies to indirect contacts as well as
direct contacts.
